Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-11 emsoft-2019/Cont_Syn.tex
Controller Syn.

 while True:
   F,G,H,K = design_robust_MPC((*$\delta$*))
   errorChoise = incorrect_region_error(F,G,H,K,(*$\varepsilon$*))
   if (*$\delta$*) > errorChoise:
     errorAct = (*$\delta$*) - errorChoise
     precision_tuning(F, G, errorAct)
     precision_tuning(H, K, (*$\varepsilon$*))
     break
   else:
     (*$\delta$*)=errorChoise+(*$\varepsilon_{SAFE}$*)
\end{lstlisting}
\caption{design of robust MPC with precision tuning}
\label{lst:alg}
\end{figure}

@@

From line 1 to 3, the procedure waits for input parameters from the designer: $\delta$ and $\varepsilon_{Q}$. $\delta$ is the maximal disturbance coefficient the controller has to be designed for. It is a problem dependent parameter, and thus can be any positive number. Typically, it is in the order of 0.1.
$\varepsilon_{Q}$ is the imprecision error-bound for the quantization of borders. 
The latter has to be strictly greater than zero, otherwise we could rely on infinite precision for storage of borders. Usually, the value for $\varepsilon_{Q}$ is in the order of 0.001.

@@

Once input parameters are verified, in line 7 we design the controller in MATLAB MPC Toolbox. The suite receives in input the coefficient $\delta$, and the state space model for the plant (e.g. inverted pendulum or aircraft) we need to control. The suite returns a piecewise affine function (F and G) together with a polytopes region partitioning (H and K).

@@

\eva{The precision tuning, which is the main contribution of the paper is not explained.}

\subsection{Implementation}
\eva{Some notes about how this is implemented}

>>>>

 while True:
   F,G,H,K = design_robust_MPC((*$\delta$*))
   errorChoise = incorrect_region_error(F,G,H,K,(*$\varepsilon$*))
   if (*$\delta$*) > errorChoise:
     errorAct = (*$\delta$*) - errorChoise
     precision_tuning(F, G, errorAct)
     precision_tuning(H, K, (*$\varepsilon_{Q}$*))
     break
   else:
     (*$\delta$*)=errorChoise+(*$\varepsilon_{SAFE}$*)
\end{lstlisting}
\caption{design of robust MPC with precision tuning}
\label{lst:alg}
\end{figure}

@@

From line 1 to 3, the procedure waits for input parameters from the designer: $\delta$ and $\varepsilon_{Q}$. $\delta$ is the disturbance . It is a problem dependent parameter, and thus can be any positive number. Typically, it is in the order of 0.1.
$\varepsilon_{Q}$ is the imprecision error-bound for the quantization of borders. 
The latter has to be strictly greater than zero, otherwise we could rely on infinite precision for storage of borders. Usually, the value for $\varepsilon_{Q}$ is in the order of 0.001.

@@

Once input parameters are verified, in line 7 we design the controller in MATLAB multi-parametric toolbox. The suite receives in input the coefficient $\delta$, and the state space model for the plant (e.g. inverted pendulum or aircraft) we need to control. The suite returns a piecewise affine function (F and G) together with a polytopes region partitioning (H and K).

@@

%\eva{The precision tuning, which is the main contribution of the paper is not explained.}

\subsection{Implementation}
\eva{Some notes about how this is implemented}
We wrote a script Python to interface the design of the controller in MATLAB Toolbox with the precision tuning phase in Daisy. The script divides in two main components: (i) a parser to process the output from MATLAB suite and (ii) a procedure to encode the vectors F,G and H,K in expressions formatted for Daisy.
